Buildtime Trend

### 2016-01-30 buildtimetrend/btt_fosdem2016.tex
improve text
better explain packages to be used

          \item buildlog parser

@@

      \item Webservice : Free for Open Source (for now)
      \item \href{https://keen.io}{Keen.io} offered to host data for free for Open Source projects. \textbf{Thanks, guys!}

@@

      \item notification on a jumpy build job

@@

    Questions?

@@

    Dieter Adriaenssens - \href{https://twitter.com/dcadriaenssens}{\small{@dcadriaenssens}}

>>>>

          \item buildjob log parser

@@

      \item Webservice : free for Open Source (for now)
        \item \href{https://keen.io}{Keen.io} offered to host data for Open Source projects. \textbf{Thanks, guys!}
      \item Source code available on Github
        \item service : host it yourself
        \item client : implement in your build process

@@

      \item notifications

@@

@@

    \href{https://twitter.com/dcadriaenssens}{\small{@dcadriaenssens}}
